---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Analysis of DRC Monkeypox Outbreak Data, 2015-2016

[![License (for code): MIT](https://img.shields.io/badge/License (for code)-MIT-blue.svg)](https://opensource.org/licenses/MIT)
[![License: CC0-1.0](https://img.shields.io/badge/License (for data)-CC0_1.0-lightgrey.svg)](http://creativecommons.org/publicdomain/zero/1.0/)

This repository contains data and R code which are supplements to

_Enhanced surveillance of monkeypox in Bas-Uélé, Democratic Republic of Congo: the limitations of symptom-based case definitions_, by
Gaspard Mande, Innocent Akonda, Anja De Weggheleire, Isabel Brosius, Laurens Liesenborghs, Emmanuel Bottieau, Noam Ross, Guy -Crispin Gembue, Robert Colebunders, Erik Verheyen Ngonda Daulya, Herwig Leirsh, and Anne Laudisoit (2022)

Please cite that paper, and/or the Zenodo data reference (<10.5281/zenodo.6574451>)
when using or refering to this study.

## Repository Structure and Reproducibility

-   `data/` contains de-identified data from the study and a data dictionary
-   `R/` contains functions used in this analysis. 
-   `reports/` contains literate code foor  R Markdown reports generated in the analysis
-   `outputs/` contains compiled reports and figures.
-   This project uses the [{targets}](https://wlandau.github.io/targets-manual/) 
    framework to organize build steps.  The diagram of steps is below and
    is defined in the `_targets.R` file and the workflow can be executed by running
    `run.R` or `run.sh`.

    <details>
    <summary>Diagram of Pipeline Dependency Graph</summary>
    
    The code below generates a figure using `mermaid.js` and is rendered when viewing
    on GitHub
    ```{r, echo=FALSE, results='asis'}
    cat(
      "```mermaid",
      targets::tar_mermaid(targets_only = TRUE),
      "```",
      sep = "\n"
    )
    ```
    </details>


-   This project requires R 4.2.0. This project us the [{renv}](https://rstudio.github.io/renv/) framework to 
    record R package dependencies and versions. Packages used are recorded in 
    `renv.lock` and code used to manage dependencies is in `renv/` and other files
    in the root project directory.
