---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Monkeypox Clinical Diagnosis Analysis



[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.6603201.svg)](https://doi.org/10.5281/zenodo.6603201)
[![License (for code): MIT](https://img.shields.io/badge/License (for code)-MIT-blue.svg)](https://opensource.org/licenses/MIT)
[![License: CC0-1.0](https://img.shields.io/badge/License (for data)-CC0_1.0-lightgrey.svg)](http://creativecommons.org/publicdomain/zero/1.0/)

This repository contains data and R code which are supplements to:

_Enhanced surveillance of monkeypox in Bas-Uélé, Democratic Republic of Congo: the limitations of symptom-based case definitions_, by
Gaspard Mande, Innocent Akonda, Anja De Weggheleire, Isabel Brosius, Laurens Liesenborghs, Emmanuel Bottieau, Noam Ross, Guy -Crispin Gembue, Robert Colebunders, Erik Verheyen Ngonda Daulya, Herwig Leirsh, and Anne Laudisoit (2022)

Please cite that paper, and/or the Zenodo data reference (<https://dx.doi.org/10.5281/zenodo.6574451>)
when using data or referring to this study.

## Repository Structure and Reproducibility

-   `data/datbase_MPX_final_948.xls` contains data from the study
    and a data dictionary describing all variables. Data are de-indentified;
    variables collected but removed to anonymize data are described in the
    data dictionary.
-   `R/` contains functions used in this analysis. 
-   `reports/` contains literate code foor  R Markdown reports generated in the analysis
-   `outputs/` contains compiled reports and figures.
-   This project uses the [{targets}](https://wlandau.github.io/targets-manual/) 
    framework to organize build steps for analysis pipeline.  The steps are
    defined in the `_targets.R` file and the workflow can be executed by running
    `run.R` via `source("run.R")` in your R terminal or `Rscript run.R` in 
    your system shell.

```{r, echo=FALSE, message = FALSE, results='asis'}
cat(
  "```mermaid",
  targets::tar_mermaid(targets_only = TRUE),
  "```",
  sep = "\n"
)
```

-   This project requires R 4.2.0. This poject uses the [{renv}](https://rstudio.github.io/renv/) framework to 
    record R package dependencies and versions. Packages used are recorded in 
    `renv.lock` and code used to manage dependencies is in `renv/` and other files
    in the root project directory.  On starting an R session in the working directory, run `renv::restore()`
    to install R package dependencies.
    -   The package also requires [`cmdstan`](https://mc-stan.org/users/interfaces/cmdstan) 
        to be installed. (Version 2.29.2 was used). If not already installed, run `cmdstanr::install_cmdstan(version = "2.29.2")`
        after `renv::restore()`
